Titulo

### 2015-02-25 RotacionOutFlows/Paper/ms.tex
changing line endings, fixing long lines, starting to refine the outflow model description

To fully understand the observed spectra of LAEs this galaxies must be modeled.
However the resonant nature of the lines makes this a challenging task. 
Analytical solutions for the outcoming spectra in simple ISM static geometries have been dereived
\cite{Adams72, Harrington73, Neufeld90, Dijkstra06}. Recent hydrodynamical simulations have studied the outcomming spectra of LAEs
in large scale simulations, while some others have studied detailed galaxies \citep{Verhamme12}. 
Radiative transfer codes \citep{Laursen09, Verhamme06, CLARA}have been used in order to understand the effect of the 
gas kinematics in the Line, special attention have been devoted to model the presence 
of outflows in the galaxy. here different models have attempt to (name the models, shell cavities etc.)
\citep{Behrens2014}
. Most recently \cite{Garavito14} have studied in detail the effect 
of rotation on the lyman alpha line.

@@

Where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear velocity at the sphere's surface. The minus/plus sign in the $x$/$y$-component of the velocity indicates the direction of rotation. In this case we take the angular velocity in the same direction as the $\hat{k}$ unit vector.\\

@@

\subsection{Outflow Model: ThinShell}

We use the outflow model stated in \citep{Orsi12} in which the outflow consists of a homogeneous, expanding, isothermal spherical shell surrounding a central galaxy. The inner radius $R_{in}$ is related to the outer radius $R_{out}$ by the expression $R_{in} = f_{th}R_{out}$, where $f_{th}=0.9$. The temperature of the medium is assumed constant and equal to $T=10^4 K$ and it is expanding at a constant velocity \vel. This outflow is composed by dust and gas uniformly mixed described by the column density \nh and the metallicity $Z$ as follows:

@@

Where $\langle Z_{cold} \rangle$ is the average metallicity of the cold gas and it is weighted by the product of the mass of cold gas and the \lya luminosity of the disc and bulge $f_Z$. \\

We decided to choose this model for two main reasons. First, when we analyze observed spectra we can se that the line is spread around the place where line should be when already taking into account the redshift due to the distance to the LAE. This implies that the photons before escaping the composed system suffer a change in frequency themselves, which we explain by making them rebound over the inner surface of the shell such as some of them suffer blueshift and other redshift, that even small, is significant and observed.\\

The second reason is because as the space between the shell and the galaxy is said to be void, the photons that escape from it suffer the scattering process at a far distance from the center, in a way such as if they rebound the chances that it happens in the normal direction to the surface are lower than in any other model. This implies that the photons are less likely to re-enter the galaxy so there is no need to start the diffusion inside again, allowing us to divide the spectrum creation process into 2 independent events, saving computational time and simplifying the model to its best. \\

@@

The joint model consists of combining the two models that were just explained. A rotating spherical galaxy is placed at the center with a thin shell outflow surrounding it as seen in Fig. \ref{fig:model}. What happens is that the photons that escaped the galaxy enter now into the outflow with the same radial direction that they came out with. At the end only a fraction of those manage to get out of the outflow and their wavelengths are measured to find the final spectrum.\\

\begin{figure}[h!]
\begin{center}
  \includegraphics[width=0.3\textwidth]{./figures/model.png}
\end{center}
\caption{\textbf{Model:} A central rotating galaxy surrounded by an expanding thin shell outflow.\\
\label{fig:model}}
\end{figure}

In order to simulate all the possible cases we set some key parameters for the program to vary, and some others fixed which are defined by the characteristics of LAEs. This are chosen as follows.\\

@@

For the first stage there are two fixed parameters: the optical depth $\tau = 10^8$ and the galaxy rotation velocity $v_{gal}=100$ \kms. For the second stage there is one fixed parameter: the metallicity of the outflow $Z=-4.0$. This 3 fixed values are selected because the characteristics of observed LAEs, especially their low mass and their highest star formation rate of all.\\

@@

We have then 3 parameters left that are going to vary along a wide range. These are: the galaxy viewing angle \ang, the hydrogen column density \nh and the outflow expanding velocity \vel. \\

>>>>

To fully understand the observed spectra of LAEs this galaxies must be
modeled. 
However the resonant nature of the lines makes this a challenging
task.  
Analytical solutions for the outcoming spectra in simple ISM static
geometries have been derived \cite{Adams72, Harrington73, Neufeld90,
  Dijkstra06}. Recent hydrodynamical simulations have studied the
outcomming spectra of LAEs in large scale simulations, while some
others have studied detailed galaxies \citep{Verhamme12}.  
Radiative transfer codes \citep{Laursen09, Verhamme06, CLARA}have been
used in order to understand the effect of the  gas kinematics in the
Line, special attention have been devoted to model the presence   of
outflows in the galaxy. here different models have attempt to (name
the models, shell cavities etc.) 
\citep{Behrens2014}. 
Most recently \cite{Garavito14} have studied in detail the effect 
of rotation on the lyman alpha line.

@@

Where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear
velocity at the sphere's surface. The minus/plus sign in the
$x$/$y$-component of the velocity indicates the direction of
rotation. In this case we take the angular velocity in the same
direction as the $\hat{k}$ unit vector.

@@

\subsection{Outflow Model: Thin Shell}

We use the outflow model stated in \citep{Orsi12}. 
In their model the outflow consists of an homogeneous, expanding,
isothermal spherical shell surrounding a central galaxy.   
This model is completly described by three sets ot paremeters that
define the geometry, kinematics and thermodinamics of the model.
The geometry is described by the shell's inner radius $R_{in}$ and outer
radius $R_{out}$, which are related to each other by the expression
$R_{in} = f_{th}R_{out}$, with $f_{th}=0.9$ as the fiducial value. 
The temperature of the medium is assumed constant
and equal to $T=10^4 K$ and it is expanding at a constant velocity
\vel. This outflow is composed by dust and gas uniformly mixed
described by the column density \nh and the metallicity $Z$ as
follows:

@@

Where $\langle Z_{cold} \rangle$ is the average metallicity of the
cold gas and it is weighted by the product of the mass of cold gas and
the \lya luminosity of the disc and bulge $f_Z$.

We decided to choose this model for two main reasons. First, when we
analyze observed spectra we can se that the line is spread around the
place where line should be when already taking into account the
redshift due to the distance to the LAE. This implies that the photons
before escaping the composed system suffer a change in frequency
themselves, which we explain by making them rebound over the inner
surface of the shell such as some of them suffer blueshift and other
redshift, that even small, is significant and observed.

The second reason is because as the space between the shell and the
galaxy is said to be void, the photons that escape from it suffer the
scattering process at a far distance from the center, in a way such as
if they rebound the chances that it happens in the normal direction to
the surface are lower than in any other model. This implies that the
photons are less likely to re-enter the galaxy so there is no need to
start the diffusion inside again, allowing us to divide the spectrum
creation process into 2 independent events, saving computational time
and simplifying the model to its best.

@@

The joint model consists of combining the two models that were just
explained. A rotating spherical galaxy is placed at the center with a
thin shell outflow surrounding it as seen in
Fig. \ref{fig:model}. What happens is that the photons that escaped
the galaxy enter now into the outflow with the same radial direction
that they came out with. At the end only a fraction of those manage to
get out of the outflow and their wavelengths are measured to find the
final spectrum.

\begin{figure}[h!]
\begin{center}
  \includegraphics[width=0.3\textwidth]{./figures/model.png}
\end{center}
\caption{\textbf{Model:} A central rotating galaxy surrounded by an expanding thin shell outflow.
\label{fig:model}}
\end{figure}

In order to simulate all the possible cases we set some key parameters
for the program to vary, and some others fixed which are defined by
the characteristics of LAEs. This are chosen as follows.

@@

For the first stage there are two fixed parameters: the optical depth
$\tau = 10^8$ and the galaxy rotation velocity $v_{gal}=100$ \kms. For
the second stage there is one fixed parameter: the metallicity of the
outflow $Z=-4.0$. This 3 fixed values are selected because the
characteristics of observed LAEs, especially their low mass and their
highest star formation rate of all.

@@

We have then 3 parameters left that are going to vary along a wide
range. These are: the galaxy viewing angle \ang, the hydrogen column
density \nh and the outflow expanding velocity \vel.
